I don't know, are you sure you want to do this?

### 2016-10-10 submission/paper.tex
Added confidence interval figure for Bergen

\begin{figure}
\begin{center}
\includegraphics[width=39pc]{bergen_ci.png}
\caption{ }
\label{fig:ci}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=39pc]{bergen_ci.png}
\caption{Simultaneous 90\% confidence set (thick black lines) for Bergen sea level projections for the years 2000-2100 using RCP8.5. The sea level data are shown in blue and end in 2015. The thin red lines are the projections without uncertainty based on each of the climate models. The dashed purple lines connect pointwise confidence intervals for each year. }
\label{fig:ci}
\end{center}
\end{figure}
